---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mathR

<!-- badges: start -->
<!-- badges: end -->

The goal of mathR is to provide convenience functions for basic algebraic operations including root finding, line-line intersection, and modular arithmetic for polynomials. All three functions are applied on polynomials in the real number domain.


## Installation

You can install the development version of mathR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ADC-405-S26/mathR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
devtools::install_github("ADC-405-S26/mathR")

library(mathR)
```
#### example_data table

```{r}
example_data <- data.frame(example_data)
```


#### root_finding example

```{r}
func <- example_data$maxdeg2_func[[1]]
paste0(func[1],"x^2 + ",func[2],"x + ",func[3])

root_finding(func[1],func[2],func[3])
```

#### line_line_intersection example

```{r, fig.align='center'}
param <- example_data$param_graph
line_line_intersection(param[1],param[2],param[3],param[4],param[5],param[6],param[7],param[8],param[9])
```

#### modular_arithmetic_for_function example

```{r}
modular_arithmetic_for_function(example_data$rand_func[[1]],example_data$modular[2])
```
