---
title: "Introduction to mathR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to mathR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The `mathR` provides convenience functions for some basic algebraic tasks. 

The `root_finding()` function is motivated by the quadratic formula in determining the roots of reducible degree 2 polynomials with one variable. It should demonstrates the neatness and power of the quadratic formula because when we get to degree 3 polynomials, finding roots is no longer a simple task. 

The second function, `line_line_intersection()` could be said to come out of the first function. As one thinks of the roots of a function, one can extend that idea to multiple functions. The intersections between them, if exist, are the roots of the difference function `(f1(x)-f2(x))`. The package incorporates the `ggplot2` package which helps create a visualization of polynomial functions with the `rootSolve` package that can handle root finding for degree 3 polynomials to return a plot of the intersections between two polynomials inside the user's interested x-interval. Because line-line intersection is highly used in Economics, users in this field could find this function helpful.

Lastly, the `modular_arithmetic_for_function()` function is motivated by the subject of rings and fields. A core concept users will encounter in this subject is the abstract idea of categorical objects: to understand an object, you do not have to look inside it but rather study its relationship with objects that are already well-understood. Thus, modular arithmetic provides the tool to travel from a bigger ring to a smaller one, one which we can understand, and hence, on the subject of polynomials, it seems fit within the scope of this package.

## Workflow

To install this package from GitHub, use

```{r, eval=FALSE}
# install.packages("remotes")
# install.packages("devtools")
devtools::install_github("ADC-405-S26/mathR")
```


Load the package using the following code.

```{r setup}
library(mathR)
```

The package contains three functions

* `root_finding`

This function returns the roots of a polynomial of one variable x whose maximum degree is 2 and coefficients are in the Real domain.


```{r}
func <- example_data$maxdeg2_func[[1]]
paste0(func[1],"x^2 + ",func[2],"x + ",func[3])

root_finding(func[1],func[2],func[3])
```


* `line_line_intersection`

This function takes two polynomials of one variable x whose maximum degree is 3 and coefficients are in the Real domain. It returns a graph of the functions and the coordinates of their intersections within the user's specified x-interval. 

If you just want to visualize a degree 2 polynomial and its root from the first example here, you can make the parameters for the second function all zero and start with a wide interval. If the roots appear close to the origin, you then zoom into the origin by reducing the size of your interval. 


```{r, fig.align='center'}
param <- example_data$param_graph
func1 <- paste0(param[1],"x^3 + ",param[2],"x^2 + ",param[3],"x + ",param[4])
func1

func2 <- paste0(param[5],"x^3 + ",param[6],"x^2 + ",param[7],"x + ",param[8])
func2

interval <- param[9]
paste0('(',-interval,',', interval,')')

line_line_intersection(param[1],param[2],param[3],param[4],param[5],param[6],param[7],param[8],param[9])
```

* `modular_arithmetic_for_function`

This function applies modular arithmetic to polynomials whose coefficients are in the Real domain.

```{r}
modular_arithmetic_for_function(example_data$rand_func[[1]],example_data$modular[2])
```
