---
title: "Introduction to mathR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to mathR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The `mathR` provides convenience functions for some basic algebraic tasks. 

The `root_finding()` function is motivated by the quadratic formula in determining the roots of reducible degree 2 polynomials with one variable. It should demonstrates the neatness and power of the quadratic formula because when we get to degree 3 polynomials, finding roots is no longer a simple task. 

The second function, `line_line_intersection()` could be said to come out of the first function. As one thinks of the roots of a function, one can extend that idea to multiple functions and the intersections between them, if exist, are the roots of the difference function `(f1(x)-f2(x))`. The package incorporates the ggplot2 package which helps create a visualization of polynomial functions with the rootSolve package that can handle root finding for degree 3 polynomials to return a plot of the intersections between two polynomials inside the user's interested x-interval. Because line-line intersection is highly used in Economics, users in this field could find this function helpful.

Lastly, the `modular_arithmetic_for_function()` function is motivated by the subject of rings and fields. A core concept users will encounter in this subject is the abstract idea of categorical objects: to understand an object, you do not have to look inside it but rather study its relationship with objects that are already well-understood. Thus, modular arithmetic provides the tool to travel from a bigger ring to a smaller one, one which we can understand, and hence, on the subject of polynomials, it seems fit within the scope of this package.

## Workflow

To install this package from GitHub, use

```{r, eval=FALSE}
# install.packages("remotes")
# install.packages("devtools")
devtools::install_github("ADC-405-S26/mathR")
```


Load the package using the following code.

```{r setup}
library(mathR)
```

The package contains three functions

* `root_finding`

This `root_finding()` function returns the roots of a polynomial of one variable x whose maximum degree is 2 and coefficients are in the Real domain.



* `line_line_intersection`

This `line_line_intersection()` function takes two polynomials of one variable x whose maximum degree is 3 and coefficients are in the Real domain. It returns a graph of the functions and the coordinates of their intersections within the user's specified x-interval. 

* `modular_arithmetic_for_function`
